---
title: "MATH 216 Homework 5"
author: "Christian Lehner"
output: html_document
---


## Admistrative:

Please indicate

* Who you collaborated with:Phil Hoxie
* Roughly how much time you spent on this HW: 6
* What gave you the most trouble: Phil's Humor / Creating the Shiny App
* Any comments you have: How long will we have access to our middlebury shiny server?





## Question 1:

* Pick three books from [Project Gutenberg](https://www.gutenberg.org/) and make
a "single-file" Shiny app based on file `App.R`
    + showing the corresponding wordcloud for a given book
    + that has "toggle" functionality to switch between the three books
* Note: Project Gutenberg tends to have older books whose copyright has expired.
* Install all necessary packages on your Middlebury Shiny server account
following the instructions given in Lec16 Shiny.
* Upload your app to the Middlebury Shiny server and replace the NHL link with
the link for your app [here](https://shiny.middlebury.edu:3838/clehner/Words/), so that when you Knit the 
document a working hyperlink shows.

Hints:

* Get your code completely working for a non-Shiny app first, then build your
app slowly.
* If you get stuck, please ask for help sooner rather than later. I don't want 
people spinning their wheels on this HW this late in the semester.
* Consider using `if` and `else` statements to switch out which text to show the
wordcloud for. Note this isn't the only way to do this. Ex:

```{r}
text <- "blah2"
if(text == "blah1"){
  value <- 1
} else if (text == "blah2"){
  value <- 2
} else if (text == "blah3"){
  value <- 3
}
value
```

```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(stringr))
suppressPackageStartupMessages(library(tm))
suppressPackageStartupMessages(library(wordcloud))
suppressPackageStartupMessages(library(SnowballC))
```

```{r}
value <- 3
if(value == 1){
  value <- "words/Tale_of_Two_Cities"
} else if (value  == 2) {
  value <- "words/Ulysses"
} else if (value  == 3){
  value <- "words/The_Adventures_of_Sherlock_Holmes"
}

book <-
  readLines(value, encoding="UTF-8") %>%
  as.character()
book <- book %>%
  tolower() %>%
  removeNumbers() %>%
  removePunctuation() %>%
  removeWords(stopwords("english")) %>%
  stemDocument() %>%
  stripWhitespace()

book <- VectorSource(book) %>% 
  Corpus()

wordcloud(book, scale=c(5,0.5), max.words=25, random.order=FALSE,
          rot.per=0.35, use.r.layout=FALSE, colors=brewer.pal(8, "BuPu"))
```

>There are differences in the use of words, clearly we would want to remove names, places etc to see the differences more clearly. I also ran into some issues uploading the shiny app to middleburys server but I got it to work.













